Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-06-26 doc/manuscript_hkk_drought_sensitivity.Rmd
Update manuscript_hkk_drought_sensitivity.Rmd
@krishnaanujan , pushing one small edit where I commented out a part that wasn't clear to me. You may want to clarify/ reinstate.

The droughts analysed had distinct climatic and temporal characteristics, with 2010 primarily a dry-season drought, 2015 a wet-season drought and 2020 showing mixed characteristics (Table 1, Fig `r fig_droughts`).
The 2010 drought showed 30-day-mean meteorological anomalies between February and May including lower precipitation (min anomaly **<-1** SD), higher number of dry days (anomaly **~1.5** SD), higher maximum temperature (anomaly **>2** SD), and higher VPD (anomaly **>2** SD), including in the wet-season.
<!-- Multi-month SPEI values reached their minima in May, after which unusually wet conditions led to a fairly rapid recovery to normal conditions. -->
1- to 6-month SPEI values reached minima between -1.5 and -2, indicative of severe drought, while the 12-month values remained above -1, indicative of mild drought. 
In 2015, pronounced meteorological anomalies on the 30-day scale occurred during the wet-season, including precipitation (anomaly **<-1.5** SD), number of dry days (max anomaly **>2** SD), maximum monthly temperatures (anomaly **+1.5** SD), and monthly maximum VPD (max anomaly **+2** SD).
<!-- 1-month SPEI was <-1 in May and June, reaching -2 in May, the lowest in the the entire dendroband census period.  -->
<!-- Multi-month SPEI values reached their minima between June and August and remained negative into the subsequent dry season. -->
1- to 12-month SPEI values crossed minima -2, lowest in the dendroband census period and indicative of severe drought. 
In 2020, meteorological anomalies were pronounced both in the dry- and wet-seasons, including maximum temperature (**>2** SD) and VPD (**>2** SD). 
3- and 6-month SPEI values reached minima ~2 in February, indicative of borderline severe drought.
12-month SPEI showed severe drought conditions from January to April, and moderate drought from May to September, spanning both dry- and wet-seasons.

>>>>

The droughts analysed had distinct climatic and temporal characteristics, with 2010 primarily a dry-season drought, 2015 a wet-season drought and 2020 showing mixed characteristics (Table 1, Fig `r fig_droughts`).
In 2010, 30-day-mean meteorological anomalies between February and May included lower precipitation (min anomaly **<-1** SD), higher number of dry days (anomaly **~1.5** SD), higher maximum temperature (anomaly **>2** SD), and higher VPD (anomaly **>2** SD)<!--, including in the wet-season [KAT: commenting this out because I find it unclear/ don't understand what it means]-->.
<!-- Multi-month SPEI values reached their minima in May, after which unusually wet conditions led to a fairly rapid recovery to normal conditions. -->
1- to 6-month SPEI values reached minima between -1.5 and -2, indicative of severe drought, while the 12-month values remained above -1, indicative of mild drought. 
In 2015, pronounced meteorological anomalies on the 30-day scale occurred during the wet-season, including precipitation (anomaly **<-1.5** SD), number of dry days (max anomaly **>2** SD), maximum monthly temperatures (anomaly **+1.5** SD), and monthly maximum VPD (max anomaly **+2** SD).
<!-- 1-month SPEI was <-1 in May and June, reaching -2 in May, the lowest in the the entire dendroband census period.  -->
<!-- Multi-month SPEI values reached their minima between June and August and remained negative into the subsequent dry season. -->
1- to 12-month SPEI values crossed minima -2, lowest in the dendroband census period and indicative of severe drought. 
In 2020, meteorological anomalies were pronounced both in the dry- and wet-seasons, including maximum temperature (**>2** SD) and VPD (**>2** SD). 
3- and 6-month SPEI values reached minima ~2 in February, indicative of borderline severe drought.
12-month SPEI showed severe drought conditions from January to April, and moderate drought from May to September, spanning both dry- and wet-seasons.
